---
output:
  html_document: default
  pdf_document: default
---
Wine Data Exploration by Yijian Zong
========================================================


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.
library(knitr)
library(ggplot2)
library(gridExtra)
library(RColorBrewer)
library(psych)
knitr::opts_chunk$set(fig.width=9,fig.height=6,fig.path='Figs/',
                      fig.align='center',tidy=TRUE,
                      echo=FALSE,warning=FALSE,message=FALSE)
```

## reading data
```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd("C:/Users/yizong/Downloads")
wine <- read.csv('wineQualityReds.csv')

```


This dataset includes information about red wines such as density, PH, and corr
esponding quality score.

# Univariate Plots Section


## Variable Check
```{r echo=FALSE, Univariate_Plots}
str(wine)
```

```{r echo=FALSE, Univariate_Plots2}
dim(wine)
```

Our dataset consists of 13 variables, with almost 1600 observations. 

## Summary of data

First, I added one more variable quality.f as a factor variable for quality
for the ease of analysis.

```{r echo=FALSE, Univariate_Plots3}
wine$quality.f <- factor(wine$quality)
summary(wine)
```

Look at the summary, we know the majority of wine is in good quality. Density
has very narrow range, which means it might not be a good predictor of quality.
Let's explore the variables to make more useful discoveries. 

Show levels of quality after factor transformation 

```{r echo=FALSE, Univariate_Plots4}
levels(wine$quality.f )
```

There are six types of quality from 3 to 8 in ascending order.

## Table of wine

```{r echo=FALSE, Univariate_Plots5}
table(wine$quality)
```
We see that wine of quality of 5,6 have the highest frequency. 

## Histogram of quality of wine 

```{r echo=FALSE, Univariate_Plots6}
qplot(x=quality.f, data=wine)+
  scale_x_discrete(breaks=3:8)
```

As we can see, the quality is almost normally distributed, which means it is a
good representation of population.

## Name of variables

```{r echo=FALSE, Univariate_Plots7}
names(wine)
```

After addition of factor variable quality.f, now we have 14 variables.

## Histogram of pH of wine faceted by quality
```{r echo=FALSE, Univariate_Plots8}

qplot(x=pH, data=wine)+
  scale_x_discrete(breaks=3:8)+
  facet_wrap(~quality.f,ncol=3)

```

After wrapping the histogram of pH by quality, we can see pH is normally 
distributed across the quality 4,5,6,7. This means the amount of pH is not 
affected by the wine quality in those groups.

```{r echo=FALSE, Univariate_Plots9}
qplot(x=density, data=wine)
```

Density without transformation is nearly normally distributed, which means the samples resemble the population in a large extent. 

```{r echo=FALSE, Univariate_Plots10}
qplot(x=alcohol, data=wine)
```

The alcohol distribution is right skewed, meaning that its mean is higher
than the median. In the next step, we try to log transform it to explore 
deeper. 

```{r echo=FALSE, Univariate_Plots11}
p1 <- qplot(x=log10(alcohol+1), data=wine)
p2 <- qplot(x=sqrt(alcohol), data=wine)

grid.arrange(p1,p2,ncol=1)
```

As we see, even after the transformation of scale, alcohol is still right skewed
.

```{r echo=FALSE, Univariate_Plots13}
qplot(x=residual.sugar, data=wine, binwidth=2)+
  scale_x_continuous(limits = c(1,18))
```

The histogram of residual sugar is also right skewed, just like alcohol. 

```{r echo=FALSE, Univariate_Plots14}
qplot(x=residual.sugar, data=wine, binwidth=0.1)+
  scale_x_continuous(limits = c(1,18),breaks=seq(0,16,1))
  
```


```{r echo=FALSE, Univariate_Plots15}
summary(wine$residual.sugar)
  
```

The summary justifies the plot and the outlier 15.5 drags the mean higher than 
the median. 

After plotting the data with different bins width, 
we can see most of the residual sugar lie between 1 and 3, with a median of 2.2. 

```{r echo=FALSE, Univariate_Plots16}
qplot(x=residual.sugar, data=subset(wine,wine$residual.sugar<15.5), binwidth=2)+
  scale_x_continuous(limits = c(1,18))
```
After trimming the highest residual sugar, we can see the plot is still very similar to the above plot. 

```{r echo=FALSE, Univariate_Plots17}
qplot(x=free.sulfur.dioxide, data=wine)
```

The histogram of free sulfur dioxide is right skewed. 

```{r echo=FALSE, Univariate_Plots18}
qplot(x=total.sulfur.dioxide, data=wine)
```

The histogram of total sulfur dioxide is right skewed. 

```{r echo=FALSE, Univariate_Plots20}
summary(wine$total.sulfur.dioxide)
```

As we see, the highest of total sulfur dioxide is 289, yet the median is only
38.00, thus creating a right skewed distribution.

```{r echo=FALSE, Univariate_Plots21}
qplot(x=log(total.sulfur.dioxide+1), data=wine,binwidth=0.25)
```

After log transformation, we now see the pattern, total sulfur dioxide has a 
bimodal distribution, cluttered on 3.25 and 3.75.

```{r echo=FALSE, Univariate_Plots22}
qplot(x=log(free.sulfur.dioxide+1), data=wine,binwidth=0.25)
```

The very similar distribution is observed after making a log transformation
to free sulfur dioxide.

```{r echo=FALSE, Univariate_Plots23}
qplot(x=log(free.sulfur.dioxide+1), data=wine,binwidth=0.01)
```

After shrinking the binwidth, we can see most wine cluttered around 2 in the 
scale of log of free sulfur dioxide.

```{r echo=FALSE, Univariate_Plots24}
qplot(x=log(free.sulfur.dioxide+1), data=wine,binwidth=0.25)+
  scale_x_continuous(limits = c(0,5), breaks= seq(0,5,0.2))
```

```{r echo=FALSE, Univariate_Plots25}
qplot(x=log(total.sulfur.dioxide+1), data=wine,binwidth=0.25)+
  scale_x_continuous(limits = c(0,6), breaks= seq(0,6,0.3))
```

```{r echo=FALSE, Univariate_Plots26}
qplot(x=log(total.sulfur.dioxide+1), data=wine,binwidth=0.01)
```

Transform the long tail data to understand distribution of free and total 
sulfur dioxide.  After adding limit and breaks, we can see for the total free 
dioxide, it peaks around 3.15 and 3.9 while there is a gap between 5.1 and 5.7. 
I wonder there might be a relationship between the gaps in both graphs. 


```{r echo=FALSE, Univariate_Plots27}
qplot(x=total.sulfur.dioxide, data=subset(wine,wine$quality=='8'),binwidth=0.25)+
  ggtitle("Best Quality total sulfur dioxide distribution")
```

Most wine have total sulfur dioxide between 0 and 25.

```{r echo=FALSE, Univariate_Plots28}
summary(wine$quality=='8')
```

We can see there are 18 wine that have the highest quality in our data.


```{r echo=FALSE, Univariate_Plots29}
summary(subset(wine$total.sulfur.dioxide, wine$quality=='3'))
```

This is the Worst quality total sulfur dioxide summary

```{r echo=FALSE, Univariate_Plots30}
summary(subset(wine$total.sulfur.dioxide, wine$quality=='8'))
```
This is the Best quality total sulfur dioxide summary. As we see the higher 
quality wine tends to have higher total sulfur dioxide.

```{r echo=FALSE, Univariate_Plots31}
qplot(x=total.sulfur.dioxide, data=subset(wine,wine$quality=='3'),binwidth=0.25)+
  ggtitle("Worst Quality total sulfur dioxide distribution")
```


```{r echo=FALSE, Univariate_Plots32}
summary(wine$quality=='3')
```

There are 10 wines that have the worst quality.

```{r echo=FALSE, Univariate_Plots33}
qplot(x=free.sulfur.dioxide, data=subset(wine,wine$quality=='8'),binwidth=0.25)+
  ggtitle("Best Quality free sulfur dioxide distribution")
```

Now we turn to free sulfur dioxide analysis. As we see, most wine are cluttered
around 0 and 10, for the best quality.


```{r echo=FALSE, Univariate_Plots34}
summary(subset(wine$free.sulfur.dioxide, wine$quality=='8'))
```

This is Best quality free sulfur dioxide summary. 

```{r echo=FALSE, Univariate_Plots35}
summary(subset(wine$free.sulfur.dioxide, wine$quality=='3'))
```

This is Worst quality free sulfur dioxide summary

```{r echo=FALSE, Univariate_Plots36}
qplot(x=free.sulfur.dioxide, data=subset(wine,wine$quality=='3'),binwidth=0.25)+
  ggtitle("Worst Quality free sulfur dioxide distribution")
```

It seems that the better the wine, the more free and total sulfur dioxide 
it would have. 


```{r echo=FALSE, Univariate_Plots37}
qplot(x=fixed.acidity, data=wine, binwidth=0.5)
```

We can see fixed.acidity have an slightly right skewed distribution.

```{r echo=FALSE, Univariate_Plots38}
qplot(x=volatile.acidity, data=wine, binwidth=0.1)
```

The distribution of volatile acidity has a bimodal distribution.

```{r echo=FALSE, Univariate_Plots39}
qplot(x=citric.acid, data=wine, binwidth=0.05)
```

The distribution of citric acidis slightly right skewed. 

```{r echo=FALSE, Univariate_Plots40}

qplot(x=fixed.acidity, data=wine)+
  facet_wrap(~quality.f,ncol=3)

```

After wrapping fixed.acidity by quality, we see the fixed acidity in quality of
5 and 6 share very similar distribution. Yet, the general right skewed 
distribution is lost in quality of 7. 

```{r echo=FALSE, Univariate_Plots50}

qplot(x=volatile.acidity, data=wine)+
  facet_wrap(~quality.f,ncol=3)

```

After wrapping volatile.acidity by quality, we see the volatile acidity in quality of
5, 6, and 7 share very similar distribution.

```{r echo=FALSE, Univariate_Plots51}

qplot(x=citric.acid, data=wine)+
  facet_wrap(~quality.f,ncol=3)

```

After wrapping citric.acid by quality, we see the citric acid in quality of
5, 6 share very similar distribution.Yet the distribution seems to be normal 
in quality of 7.

```{r echo=FALSE, Univariate_Plots52}
qplot(x=sulphates, data=wine, binwidth=0.05)
```

The distribution of sulphates is very similar to that of fixed acidity.
There might be an implicit connections between two.



# Univariate Analysis

### What is the structure of your dataset?

There are 1599 wines in the dataset with 12 features(fixed.acidity, volatile.
acidity, citric acid, residual sugar, chlorides, free.sulfur.dioxide,
total.sulfur.dioxide,density, alcohol, sulphates, quality). One variable 
quality is transormed into factor variable, quality.f with the following levels:

(worst)___________>(best)
Quality: 3,4,5,6,7,8

Other observations:
* There are 18 wines that have the highest quality and 10 the lowest. 
* Mean Ph is 3.31. 
* The distribution of sulphates is very similar to that of fixed acidity.
* The maximum residual sugar is 15.5

### What is/are the main feature(s) of interest in your dataset?
The main features are quality and density. I like to determine what features
determine the quality of a wine. I suspect density and some combinations
of other variables can be used to build a predictive model to classify
wine. 
### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

density, pH, alcohol, residual sugar and total sulfur dioxide likely contribute 
to the quality. I think density and pH and toatl sulfur dioxide contribute the
most.


### Did you create any new variables from existing variables in the dataset?
I create a factor variable quality.f as a analysis metric since it is a 
categorical variable. The levels of quality are respresnted by the original
int. 

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I log transformed total.sulfur.dioxide and free.sulfur.dioxide which were 
previously right-skewed. The data after transformation is bimodal. For the free 
sulfur dioxide, it peaks around 2.0 and 2.8, while there is a gap between 1.2
and 1.4. For the total free dioxide, it peaks around 3.15 and 3.9 while there 
is a gap between 5.1 and 5.7. I did this to find underlying patterns of skewed
data. I also log-transformed alcohol, yet the distributions before and after 
look alike. 


# Bivariate Plots Section


```{r echo=FALSE, Bivariate_Plots}
cor(wine[,c(2,3,4,5,6,7,8,9,10,11,12,13)])

```

We see that alcohol has a moderate and positive correlation with wine. 

```{r echo=FALSE, Bivariate_Plots2}
library(GGally)
theme_set(theme_minimal(20))

set.seed(1836)
wine_subset <- subset(wine, select = -c(X,quality.f))
names(wine_subset)
```

We take a subset of wine excluding the the X and quality.f variables.

```{r echo=FALSE, fig.width=9,fig.height=9, Bivariate_Plots3}
ggpairs(wine_subset)+
    theme( strip.text = element_text(size = 7),
         axis.text = element_text(size = 7))
```

We see pH and fixed acidity have the highest negative correlation, followed
by citric acid and fixed acidity. After some research, I found acid in wine is 
responsible for the crisp taste. However, the acids in the data have very low
correlation with quality. So what feature is related to high quality?

```{r echo=FALSE,fig.width=9,fig.height=9,  Bivariate_Plots5}
pairs.panels(wine_subset, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )
```

After using a more clear visualization, we see alcohol has the highest 
correlation with quality. However, the correlation 0.48 is still not high 
enough. After research I know alcohol contributes to the flavour. Maybe the 
level of alcohol is related to the quality of wine?

```{r echo=FALSE, Bivariate_Plots6}
ggplot(aes(x=alcohol, y=quality),data=wine)+
  geom_jitter(alpha=0.5, width = 0, height = 0.25)
```



```{r echo=FALSE, Bivariate_Plots9}
qplot(alcohol, quality, data= wine)+
  scale_x_continuous(trans = "log10")+
  geom_jitter(alpha=0.5, width = 0, height = 0.25)+
  ggtitle('Adjusted Quality by fixed acidity(log10)')
```

The first plot shows overplotting. After adjustment by adding jitter and 
changing transparency, we still can see that the data is over-dispersed. 

```{r echo=FALSE, Bivariate_Plots10}
ggplot(aes(x=density, y=quality),data=wine)+
  geom_jitter(alpha=0.5, width = 0, height = 0.25)
```


Density distribution is similar to that of alcohol.

```{r echo=FALSE, Bivariate_Plots11}
qplot(fixed.acidity, density, data= wine)+
  scale_y_continuous()+
  ggtitle('Density by fixed acidity')
```

We there is a clear positive relationship between fixed.acidity and density.
In fact, the typical concentration of fixed acid in wine is 6000 mg/L, which is
quite big, only second to Glycerol.

```{r echo=FALSE, Bivariate_Plots13}
qplot(citric.acid , pH, data= wine)+
  scale_y_continuous()+
  ggtitle('pH by citric acid')
```

We can see pH is negatively related to citric acid. This no surprise since
the higher the acid, the lower the pH.

```{r echo=FALSE, Bivariate_Plots14}
qplot(fixed.acidity , pH, data= wine)+
  scale_y_continuous()+
  ggtitle('pH by fixed acidity')
```

Same trend has been observed in the plot of pH vs fixed acidity.

```{r echo=FALSE, Bivariate_Plots15}
qplot(volatile.acidity , pH, data= wine)+
  scale_y_continuous()+
  ggtitle('pH by volatile acidity')
```

However, the trend is lost when we plot pH vs volatile acidity.\

In general, We see there is a negative strong correlation between citric acid 
and pH
which is not surprising since the more acidic a solution is, the lower pH it 
has. The same siuation applies to other acid metrics like fixed.acidity. 
However, volatile acidity doesn't show such correlation.

```{r echo=FALSE, Bivariate_Plots16}
lmfit = lm(formula = quality ~ alcohol, data=wine)
summary(lmfit)
```

We can see this refutes our previous hypothesis that alcohol is related to 
quality since it only explains 22.63% of the variance. 

```{r echo=FALSE, Bivariate_Plots19}

lmfit_2 = lm(formula = quality ~ pH + fixed.acidity, data=wine)
summary(lmfit_2)

```
Still, the pH and fixed.acidity don't explained the quality well. 

```{r echo=FALSE, Bivariate_Plots20}
p_box_pH = qplot(quality.f , pH, 
      data= wine,
      geom = 'boxplot')
p_box_pH
```


The mean pH look similar across quality groups. However, a wine with higher quality tends to have smaller pH. 

```{r echo=FALSE, Bivariate_Plots27}
p_box_density = qplot(quality.f , density, 
      data= wine,
      geom = 'boxplot')
p_box_density
```

Here we see higher quality tends to have lower density. 


```{r echo=FALSE, Bivariate_Plots28}
p_box_sugar = qplot(quality.f , residual.sugar, 
      data= wine,
      geom = 'boxplot')
p_box_sugar
```

Here we see the medians of residual sugar are very similar across quality
groups, yet the middle quality groups(5,6) have many outliers that drives mean
higher than median. 

```{r echo=FALSE, Bivariate_Plots29}
p_box_total_sd = qplot(quality.f , total.sulfur.dioxide, 
      data= wine,
      geom = 'boxplot')
p_box_total_sd
```

Here we see the middle quality range have higher median total sulfur dioxide. 



# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

There are no variables that have strong correlation with win quality.
Regardless of quality, the variance in alcohol is high in each level. 
In the 
plot of quality vs alcohol, at each quality level the alcohol amount is spread
out. 

Based on the R^2 value, alcohol can only explain about 22.6%, yet other variable
such as pH did a worse job.

It has been confirmed that fixed acidity and citric acid are negatively related
to pH based on chemical domain knowledge. However, it is counterintuitive that 
volatile acidity doesn't follow such trend and even has a positive correlation.\
The correlation table justifies such behavior by showing that volatile acidity
is negatively to other two acidity metrics.

Density has a distribution across quality groups similar to alcohol. 

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

Other interesting finding is that fixed acidity is strongly positively 
correlated to fixed acidity, establishing an unexpected discovery.

### What was the strongest relationship you found?

The strongest relationship is between citric.acid and fixed.acidity. 

# Multivariate Plots Section


```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = fixed.acidity , y = pH, color= quality.f), data = wine) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
    guide = guide_legend(title = 'Quality', reverse = T,
    override.aes = list(alpha = 1, size = 2)))+
  scale_x_continuous()+
  scale_y_continuous()+
  ggtitle('pH by fixed acidity and Quality')
```


We can see higher quality wine tend to stay close on the linear line.

```{r echo=FALSE, Multivariate_Plots4}

ggplot(wine,aes(density,pH))+
  geom_point(aes(colour = quality.f))+
  ggtitle('pH by density and Quality') +
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality")
```


We plot pH vs density and quality, and we can see quality is very dispersed 
across the plot. This means certain combination of density and pH might not 
lead to certain quality of wine. Yets we see, at similar pH, lower density has
more lower quality wines. 


```{r echo=FALSE, Multivariate_Plots5}

ggplot(wine,aes(density,pH))+
  geom_point(aes(colour = quality.f))+
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality")+
  ggtitle('pH by density and Quality')
```

As wee see, most wine cluttered in group with density between 0.995 and 1
and pH between 3.0 and 3.5.

```{r echo=FALSE, Multivariate_Plots6}

ggplot(wine,aes(density,alcohol))+
  geom_point(aes(colour = quality.f))+
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality")+
  ggtitle('Alcohol by density and Quality')
```

We see lower quality wine tends to fall in section with density between
0.995 and 1.000 and alcohol between 9 and 10.

```{r echo=FALSE, Multivariate_Plots7}

ggplot(wine,aes(density,fixed.acidity))+
  geom_point(aes(colour = quality.f))+
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality")+
  ggtitle('Fixed Acidity by density and Quality')
```

As we see, wine with different are pretty dispersed across the density
axis. 

```{r echo=FALSE, Linear_Model}
library(memisc)
m1 <- lm(quality~alcohol, data=wine)
m2 <- update(m1,~.+pH)
m3 <- update(m2,~.+density)
m4 <- update(m3,~.+fixed.acidity)
m5 <- update(m4,~.+citric.acid)
mtable(m1,m2,m3,m4,m5)
```

We made a linear model to predict quality based on the most related features
we have. However, none of them explains the variance of quality well.

### From the linear model, we can see as we add more variables, the R^2 don't \
change much, which means the model doesn't explain the variance in quality well.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of 
looking at your feature(s) of interest?

* There is no single clear relationship that explains what makes a wine have a
good quality. Yet there is a pattern that lower quality wine tends to fall
in section with density between 0.995 and 1.000 and alcohol between 9 and 10.

* Through multivariate plot, we can see density and fixed density strengthened
each other. Across all quality groups, higher density is related to higher
fixed acidity, which makes sense because the more stable acid stays in wine,
the more dense it is. 

### Were there any interesting or surprising interactions between features?
One interesting interaction is the plot of pH vs density with color of quality
since I expected that certain combination of pH and density would contribute
to a quality of wine. However, quality is pretty dispersed across the plot.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

I create a linear model to predict quality. However, the highest R^2 is only
0.264, which means linear model might not be a good metrics for predicting
the quality of wine. However, some useful information can be fetched. Among
all the features in the model, pH improves the model by the most extent. 
------

# Final Plots and Summary



### Plot One

```{r echo=FALSE, Plot_One}
qplot(x=log(total.sulfur.dioxide+1), data=wine,binwidth=0.25)+
  scale_x_continuous(limits = c(0,6), breaks= seq(0,6,0.5))+
  ggtitle("Log_10 Total Sulfur Dioxide")
```


### Description One

The distribution of total sulfur dioxide appears to be bimodal on log scale.\
Perhaps, wines are divided into two ranges to sulfur dioxide amount. There is
also an gap in the upper range between 5 and 5.5.

### Plot Two
```{r echo=FALSE, Plot_Two}
qplot(fixed.acidity, density, data= wine)+
  scale_y_continuous()+
  ggtitle('Density by fixed acidity')
```

### Description Two

We see that fixed.acidity has a moderate positive relationship between density.
This raises interesting questions about what determines the density of a wine.
Fixed.acidity might be a good component.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(wine,aes(density,alcohol))+
  geom_point(aes(colour = quality.f))+
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality")+
  ylab(expression('Alcohol (% by Volume)')) +
  xlab(Density~(g/cm^{3}))+
  ggtitle('Alcohol by density and Quality')
```

### Description Three
We see lower quality wine tends to fall in section with density between
0.995 and 1.000 and alcohol between 9 and 10. This means low quality wine
could be associated with high density and low alcohol. This points to an
interesting speculation that high density might contain other unnecessary
chemicals without the presence of high alcohol.
------

# Reflection

Given that I already learned R in school, I didn't find much trouble getting 
used to the syntax. However, I had moments struggling with choosing what plots 
to use, how to understand what makes a wine high quality. I also found it 
difficult to design the plots to emphasize certain patterns in the data.\
There are many interetsing insights found in the exploration. For instances,
the fixed.acidity is positively related to citric acid, yet negatively
related to volatile acid. Both fixed and citric acid are negatively
related to pH. Moreover, fixed acid is closely related to density. The 
higher the fixed acid, the higher the density. \ 
However, I have trouble
finding a variable that is closely related to quality even after log
transformation. Yet I still find that low quality wine is associated with
low alcohol and high density. Further exploration might need bigger dataset
with more features to study what makes a good wine. For example, does other
substance like Glycerol or Amino Acids contribute to the quality. Moreover, 
does certain ratio of substance like sugar and fixed acid ratio have high 
correlation with the quality of wine? 

